### 2018-09-02 sections/data_presel.tex
more textual comments

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirement.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

>>>>

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirements.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

### 2018-09-02 sections/strategy_Hbb.tex
more textual comments

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity spectrum,
with a very small fraction of events having four or more $b$-tagged jets.

>>>>

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
with a very small fraction of events having four or more $b$-tagged jets.
